Figures and results for main manuscript

### 2021-01-15 analysis/reports/manuscript_main.Rmd
edits before hy and skme sign off

```{r first hists, fig.dim = c(7,7)}
fig_2 <- gridExtra::grid.arrange(grobs = list(

@@

  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
    xlab("") +
    ylab("")#+
    #xlab("Percentile rank of observed value relative to feasible set") +
  #  ylab("Number of communities")
), ncol = 2,
left = "Number of communities",
bottom = "Percentile rank of observed value relative to feasible set")

plot(fig_2)

@@

```{r}
pdf("figure_1.pdf", title = "Figure 1")
plot(fig_1)
dev.off()

pdf("figure_2.pdf", title = "Figure 2")
 plot(fig_2)
 dev.off()

pdf("figure_3.pdf", title = "Figure 3")
plot(fig_3)
dev.off()

pdf("figure_4.pdf", title = "Figure 4")
 plot(fig_4)
dev.off()
```

>>>>

```{r first hists, fig.dim = c(7,7)}
library(grid)
fig_2 <- gridExtra::grid.arrange(grobs = list(

@@

  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
    xlab("") +
    ylab("")#+
    #xlab("Percentile rank of observed value relative to feasible set") +
  #  ylab("Number of communities")
), ncol = 2,
left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))

@@

```{r}
pdf("figure_1.pdf", title = "Figure 1", bg = "white")
plot(fig_1)
dev.off()

pdf("figure_2.pdf", title = "Figure 2", bg = "white")
 gridExtra::grid.arrange(grobs = list(

  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
    xlab("") +
    ylab("")#+
    #xlab("Percentile rank of observed value relative to feasible set") +
  #  ylab("Number of communities")
), ncol = 2,
left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
 dev.off()

pdf("figure_3.pdf", title = "Figure 3", bg = "white")
gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Skewness") +
    xlim(0, 1),

dev.off()

pdf("figure_4.pdf", title = "Figure 4", bg = "white")
 plot(fig_4)
dev.off()
```
